---
title: "Lab1"
output: html_document
author: Group 4

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part 1
This dataset is derived from the All China Data Center which is formerly affiliated with the University of Michigan. The All China Data Center is run by the All China Marketing Research company, a private research firm. 

Shanghai and Beijing are technically municipalities (not provinces), which, according to Wikipedia, have a higher political status than provinces and are under direct control of the central government so therefore they are included in this dataset. 

Additionally, Hong Kong and Macau are not included in this dataset becuase although they are "special administrative regions" (SAR) of the PRC, SAR's are "highly autonomous and self-governing sub national subject of the People's Republic of China that is directly under the Central People's Government". In this way, Hong Kong and Macau control their own economies, are only really tied to China in terms of foreign policy and military/defense and therefore produce economic statistics through their own governments. To view Macau's economic data it can be accessed [here](https://www.gov.mo/en/about-macao-sar/statistics/). To view Hong Kong's economic data it can be accessed [here](https://www.hkeconomy.gov.hk/en/situation/index.htm).


##Explain the time periods that might be the least reliable, and maybe summarize some of the suggested methods for “correcting” things like GDP data. *Need help with this section- I have not found what time periods are the least reliable nor have I found methods?? See the comments and if you have data, please add

Generally speaking, economic statistics produced by the central government are consistently inflated in comparison to those produced locally/regionally. The central government has long evaluated local government officials on the basis of The National Bureau of Statistics of China's GDP. Because of this motivation to inflate national statistics, the socialist period (1949-1980) will include 
# probably inflated data?
the "reform and opening period" beginning in 1982 will include 
# more accurate data reflecting changes in the more-free market ?

In 2017 China established the Statistical Law Enforcement Supervision Bureau and the government issued “Regulations for Implementation of the Law on Statistics,” which were intended to enable punishment of statistics forgery. 

Statistics produced by private organizations tend to have more accurate data than those produced by the central government.
#general source for this, Phil just said this in the lab 1 prompt

Sources: 
* https://en.wikipedia.org/wiki/Economic_history_of_China_(1949%E2%80%93present)v
* https://japan-forward.com/how-trustworthy-are-chinese-statistics-china-inflates-gdp-figures-by-478-billion-in-2017/
* https://en.wikipedia.org/wiki/Macau
* https://www.forbes.com/sites/salvatorebabones/2018/02/12/china-quietly-releases-2017-provincial-gdp-figures/#799c69ed20dc

## Part 2 

# Explain interesting changes over time

# 5 Visualizations + short explanations

```{r, echo=FALSE}
object1=read.csv(file="China_EO_49to17.csv", fileEncoding = "latin1")
object2=as_tibble(object1)

object2$Year <- as.integer(object2$Year)
Year=seq(from=1949,to=2017)
object2$Year=Year
#write visualizations here
```


